### 2020-06-10 Report/aws_325ghz_study.tex
Few changes as response to questions fro Christophe.
Small change of 4ch-option and defined a second 3ch one.

\section{Overview of the 183, 229 and 325\,GHz bands}
\label{sec:overview}
% 
The simulations in this section are based on five Fascod climate scenarios
(Sec.~\ref{sec:fascod}), and performed with a fixed sensor viewing angle of
25$^\circ$. No hydrometeors are included. For simpler interpretation of the
results, the reflectivity is set to have no frequency variation, i.e.\ the same
value is applied for all bands. The reflective is varied between 0 and 0.5.
In the figures covering transmissivities and Jacobians, the specifications
of ICI is applied for 325\,GHz channels (Table~\ref{tab:fixed:chs}).

@@

[* Anders just informed us (May 29) that it would be good to avoid an IF of 1.7\,GHz, as that frequency could be used for downlink and there is a risk for
interference. The four channel option can easily be adopted to this, but what
do with the three channel one? *]

@@

\begin{table}[!t]
  \begin{minipage}[b]{0.5\linewidth}
  \centering  
  \begin{tabular}[c]{c|c|c}
    Channel & Frequency   & Bandwidth \\
    name    & [GHz] &  [MHz] \\
    \hline
    AWS-41  & 325.15$\pm$6.50 & 3000\\
    AWS-42  & 325.15$\pm$3.55 & 2500\\
    AWS-43  & 325.15$\pm$1.60 & 1200\\
    \hline
  \end{tabular}
  \end{minipage}%
  \begin{minipage}[b]{0.5\linewidth}
  \centering  
  \begin{tabular}[c]{c|c|c}
    Channel & Frequency   & Bandwidth \\
    name    & [GHz] &  [MHz] \\
    \hline
    AWS-41  & 325.15$\pm$6.60 & 2800\\
    AWS-42  & 325.15$\pm$4.05 & 1900\\
    AWS-43  & 325.15$\pm$2.35 & 1300\\
    AWS-44  & 325.15$\pm$1.20 & \phantom{0}800\\
    \hline
  \end{tabular}
  \end{minipage}  
  \caption{Preliminary specifications of AWS 325\,GHz channels, in the case of
    of three (left) and four (right) channels.}
  \label{tab:chs:prel}
\end{table}

\subsection{A four channel option}
%
The tentative four channel option in Table~\ref{tab:chs:prel} gives a broader
altitude coverage, towards higher altitudes, and offers weighting functions
roughly equally spaced in altitude (Fig.~\ref {fig:4ch:prel}). This option has
a IF range of 0.7 to 8.0\,GHz, and leaves 200\,MHz space between AWS-41 and
AWS-42 and has 100\,MHz between the other channels. Also this suggestion uses
the complete IF bandwidth.

>>>>

\section{Overview of the 183, 229 and 325\,GHz bands}
\label{sec:overview}
% 
The simulations in this section are based on five Fascod climate scenarios
(Sec.~\ref{sec:fascod}), and performed with a fixed sensor viewing angle of
25$^\circ$. No hydrometeors are included. For simpler interpretation of the
results, the reflectivity is set to have no frequency variation, i.e.\ the same
value is applied for all bands. The reflectivity is varied between 0 and 0.5
(these fixed values are only applied in this section, the bulk simulations are
using TESSEM and TELSEM for seting the surface properties).
In the figures covering transmissivities and Jacobians, the specifications
of ICI is applied for 325\,GHz channels (Table~\ref{tab:fixed:chs}).

@@

@@

\begin{table}[!t]
  \begin{minipage}[b]{0.5\linewidth}
  \centering  
  \begin{tabular}[c]{c|c|c}
    Channel & Frequency   & Bandwidth \\
    name    & [GHz] &  [MHz] \\
    \hline
    AWS-41  & 325.15$\pm$6.50 & 3000\\
    AWS-42  & 325.15$\pm$3.55 & 2500\\
    AWS-43  & 325.15$\pm$1.60 & 1200\\
    \hline
  \end{tabular}
  \end{minipage}%
  \begin{minipage}[b]{0.5\linewidth}
  \centering  
  \begin{tabular}[c]{c|c|c}
    Channel & Frequency   & Bandwidth \\
    name    & [GHz] &  [MHz] \\
    \hline
    AWS-41  & 325.15$\pm$6.60 & 2800\\
    AWS-42  & 325.15$\pm$4.10 & 1800\\
    AWS-43  & 325.15$\pm$2.40 & 1200\\
    AWS-44  & 325.15$\pm$1.20 & \phantom{0}800\\
    \hline
  \end{tabular}
%  \begin{tabular}[c]{c|c|c}
%    Channel & Frequency   & Bandwidth \\
%    name    & [GHz] &  [MHz] \\
%    \hline
%    AWS-41  & 325.15$\pm$6.60 & 2800\\
%    AWS-42  & 325.15$\pm$4.05 & 1900\\
%    AWS-43  & 325.15$\pm$2.35 & 1300\\
%    AWS-44  & 325.15$\pm$1.20 & \phantom{0}800\\
%    \hline
%  \end{tabular}
  \end{minipage}  
  \caption{Preliminary specifications of AWS 325\,GHz channels, in the case of
    of three (left) and four (right) channels.}
  \label{tab:chs:prel}
\end{table}

\subsection{A four channel option}
%
The tentative four channel option in Table~\ref{tab:chs:prel} gives a broader
altitude coverage, towards higher altitudes, and offers weighting functions
roughly equally spaced in altitude (Fig.~\ref {fig:4ch:prel}). This option has
a IF range of 0.7 to 8.0\,GHz, and leaves 200\,MHz space between all the
325\,GHz channels. Also this suggestion uses the complete IF bandwidth.

\subsection{A second three channel option}
%
Relatively late in the study Omnisys informed us about that an IF of 1.7\,GHz
should be avoided, as this frequency likely will be used for downlink of data.
The four channel option needed just a marginal change to adopt to this
constrain, while 1.7\,GHz is more or less at the centre of the three channel
option. It was then decided to formulate second three channel option avoiding 
1.7\,GHz, and the suggestion is found in Table~\ref{tab:chs:3b}.

\begin{table}[!h]
  \centering  
  \begin{tabular}[c]{c|c|c}
    Channel & Frequency   & Bandwidth \\
    name    & [GHz] &  [MHz] \\
    \hline
    AWS-41  & 325.15$\pm$6.50 & 3000\\
    AWS-42  & 325.15$\pm$3.30 & 3000\\
    AWS-43  & 325.15$\pm$1.20 & \phantom{0}800\\
    \hline
  \end{tabular}
  \caption{The second three channel suggestion.}
  \label{tab:chs:3b}
\end{table}

AWS-41 is identical between the two three channel options. In this second
option, AWS-43 is set to have the same limits as AWS-44 in the four channel
option. AWS-42 was then allowed to fill the frequency range between the two
other channels, but keeping a gap of 200\,MHz on each side.

The resulting weighting functions are exemplified in Fig.~\ref{fig:3bch:prel}.
As expected, there is now a somewhat poorer match to 183\,GHz, most importantly
the weighting function of AWS-43 ends up between the ones of AWS-35 and 36. The
weighting function of AWS-42 is slightly moved upwards compared to the first
three channel option.

\begin{figure}[!tb]
  \centering
  \includegraphics[height=61mm]{fascod_3bchopt_tro}\hspace{5mm}% 
  \includegraphics[clip,trim=43 0 0 0,height=61mm]{fascod_3bchopt_mlw}
  \caption{RH weighting functions of the second three channel option
    (Table~\ref{tab:chs:3b}), for the Fascod tropical (left) and mid-latitude
    winter (right) scenarios.}
  \label{fig:3bch:prel}
\end{figure}
